Parallel air palletization and tour planning for simultaneous pickup and delivery

### 2023-02-09 latex/comp_or.tex
Knapsack DP algorithm will be tested
bETTER RESULTS

We also created a process-based parallel computing heuristic that quickly finds good solutions for a wide range of problem sizes, an essential contribution as { \color{red} it was the unique method that managed to solve all testing scenarios.}

@@

\begin{table}[H]
\centering
\caption{Volume surpluses, methods and scenarios results}  \label{tab:results}
\footnotesize
%\scriptsize
\begin{tabular}{crcccccccc}
\toprule
&                       &                           &\multicolumn{6}{c}{\bf Scenarios}              &{\bf Normalized}\\
\cmidrule{4-9}		
{\bf Surplus}           & {$method$}                &{\bf Results}       &{\bf 1}&{\bf 2}&{\bf 3}&{\bf 4}&{\bf 5}&{\bf 6}&{\bf Speed-up} \\
\toprule

\multirow{6}{*}{$1.2$} &\multirow{2}{*}{ Gurobi}& $f$                & 9.75       &  6.34    &  7.61  &   7.43    &       &       &   \\%
&                                               & {\bf run-time (s)} &  8         &   17     &  30    &  114     &       &       &   \\%

\cmidrule{2-10}		                       
&\multirow{2}{*}{ $Shims$}                      & $f$                & 7.00       &  4.20    &  4.12  &  3.54     &       &       &   \\%
&                                               & {\bf run-time (s)} &  < 1       &   3      &    5   &   19    &       &       &   \\%

\cmidrule{2-10}		                       
&\multirow{2}{*}{ $mpShims$}                    & $f$                & {\bf 9.85} &  7.52    &  8.33  &  7.82     &       &       &   \\%
&                                               & {\bf run-time (s)} &  < 1       &  < 1     &    2   &  8     &       &       &   \\%

@@

\end{tabular}
%\textsuperscript{$Gurobi^*$ was run with a time limit of 60s per node.}	
\normalsize
\end{table}

$Gurobi^*$ was run with a time limit of 60s per node. The remaining methods were run with a time limit of 1.6s per node, the worst time {\it Shims} took to solve a node.

>>>>

We also created a process-based parallel computing heuristic that quickly finds good solutions for a wide range of problem sizes, an essential contribution as it surpassed all Shims results and some of the Gurobi results, all methods under a time limit.

@@

\begin{table}[H]
\centering
\caption{Volume surpluses, methods and scenarios results}  \label{tab:results}
\footnotesize
%\scriptsize
\begin{tabular}{crcccccccc}
\toprule
                      &                          &                    &\multicolumn{6}{c}{\bf Scenarios}              &{\bf Normalized}\\
                                                                      \cmidrule{4-9}		
{\bf Surplus}         & {$method$}               & {\bf Results}      &{\bf 1}      &{\bf 2}     &{\bf 3}      &{\bf 4}      &{\bf 5}       &{\bf 6}      &{\bf Speed-up} \\
\toprule

\multirow{7}{*}{$1.2$}&\multirow{2}{*}{ $Gurobi$}& $f$                & 12.00       & {\bf 8.38} & {\bf 12.19} & 13.38       &  14.42      &           &   \\%
                      &                          & {\it run-time (s)} &  8          &   14       &  25         &  95         &    217      &  1719       &   \\%

                      \cmidrule{2-10}		                       
                      &\multirow{2}{*}{ $Shims$} & $f$                & 8.37        &  6.40      &  7.68       &  8.05       &   7.72      & 6.74        & \\%
                      &                          & {\it run-time (s)} &  < 1        &  < 1       &    3        &   11         &   27       &  342        &\\%

                      \cmidrule{2-10}		                       
                      &\multirow{2}{*}{ $mpShims$}& $f$               & {\bf 12.24} &  7.95      &  11.59      & {\bf 13.80} & {\bf 16.16} & {\bf 13.74} &   \\%
                      &                           & {\it run-time (s)}&  < 1        &  < 1       &    2        &   6         &    15       &   165       &   \\%

@@

\end{tabular}
%\textsuperscript{asdf sd .}	
\normalsize
\end{table}

For {\it Gurobi} in {\bf Scenario 1}, 50\% of the results were optimal, but the remaining were suboptimal due to the time limit. This explains that {\it mpShims} surpassed {\it Gurobi} results. The same applies to scenarios 4, 5 and 6, where {\it Gurobi} obtained less than 30\% optimal results.
